The imprint of global magma oceans on exoplanet demographics

### 2023-03-06 src/tex/ms.tex
move M-R to new discussion section w/ impact of assumptions

% Define document class
\documentclass[twocolumn]{aastex631}
%\documentclass[modern]{aastex631}

@@

To assign masses to our planets, we use the semi-empirical mass-radius relationship derived in \citet{Zeng2016}.
The default relation our planets follow is one assuming a pure $\mathrm{MgSiO_3}$ composition.
While interior composition may change the magnitude of radius inflation and could introduce an offset to its demographic imprint, we do not expect a change of its structure and detectability.
\todo[inline]{run a test: do we expect that the choice of M-R relation impacts the results? Perhaps have an appendix section.}
This represents the baseline bulk density before any climate-related effects are applied.

@@

>>>>

% Define document class
%\documentclass[twocolumn]{aastex631}
\documentclass[modern]{aastex631}

@@

To assign masses to our planets, we use the semi-empirical mass-radius relationship assuming a pure $\mathrm{MgSiO_3}$ composition from \citet{Zeng2016}.
This represents the baseline bulk density before any climate-related effects are applied.

@@

\subsection{Impact of assumptions on our findings}
\subsubsection{Baseline mass-radius relationship}
Our baseline mass-radius relationship assuming pure $\mathrm{MgSiO_3}$ interiors~\citep{Zeng2016} might not be representative of the rocky planet population.
However, while interior composition may change the magnitude of radius inflation and could introduce an offset to its demographic imprint, we do not expect a change of its structure.
The magnitude of the radius inflation effect is in fact expected to be larger for an Earth-like interior composition with an iron core-silicate mantle structure.\todo[inline]{TIM: do you have a reference for this statement?}
We thus consider our mass-radius relationship a conservative case and do not expect a negative impact on the detectability of the runaway greenhouse transition due to deviations from it.
\todo[inline]{if feasible: run a test with a different M-R relation. do we expect that the choice of M-R relation impacts the results? Perhaps have an appendix section.}
